Space is the Place: Effects of Continuous Spatial Structure on Analysis of Population Genetic Data

### 2020-01-31 ms/spaceness.tex
added line ref

Clinal environments cause an interesting pattern in false positives after PC correction: at low neighborhood sizes the correction removes nearly all significant associations, 
but at neighborhood sizes above roughly 250 the proportion of significant SNPs increases to up to 0.4\% (Figure~\ref{fig:gwas}). 
This may be due to a loss of descriptive power of the PCs
-- as neighborhood size increases, the total proportion of variance explained by the first 10 PC axes declines from roughly 10\% to 4\% (Figure \ref{fig:gwas}B). 
Essentially, PCA seems unable to effectively summarize the weak population structure present in large-neighborhood simulations, but these populations continue to have enough spatial structure to create significant correlations between genotypes and the environment. A similar process can also be seen in the corner phenotype distribution, in which the count of significant SNPs initially declines as neighborhood size increases and then increases at approximately the point at which the proportion of variance explained by PCA approaches its minimum.

>>>>

Clinal environments cause an interesting pattern in false positives after PC correction: at low neighborhood sizes the correction removes nearly all significant associations, 
but at neighborhood sizes above roughly 250 the proportion of significant SNPs increases to up to 0.4\% (Figure~\ref{fig:gwas}). 
This may be due to a loss of descriptive power of the PCs
-- as neighborhood size increases, the total proportion of variance explained by the first 10 PC axes declines from roughly 10\% to 4\% (Figure \ref{fig:gwas}B). 
Essentially, PCA seems unable to effectively summarize the weak population structure present in large-neighborhood simulations, \revpoint{2}{2}
but these populations continue to have enough spatial structure to create significant correlations between genotypes and the environment. A similar process can also be seen in the corner phenotype distribution, in which the count of significant SNPs initially declines as neighborhood size increases and then increases at approximately the point at which the proportion of variance explained by PCA approaches its minimum.
